Reliable error estimation for Sobol' indices

### 2016-08-10 article.tex
Adding figure to estimator S in article.tex
More changes in article.tex

\newcommand{\fudge}{\fC}
\newcommand{\dtf}{\textit{\doubletilde{f}}}
\newcommand{\cube}{[0,1)^d}
%\renewcommand{\bbK}{\natzero^d}
\newcommand{\rf}{\mathring{f}}
\newcommand{\rnu}{\mathring{\nu}}
\newcommand{\natm}{\naturals_{0,m}}
\newcommand{\wcS}{\widecheck{S}}
\newcommand{\tol}{\text{tol}}
\newcommand{\e}{\text{e}}
\newcommand{\bvec}[1]{\boldsymbol{#1}}
\newcommand{\vx}{\bvec{x}}
\newcommand{\vI}{\bvec{I}}
\newcommand{\vk}{\bvec{k}}
\newcommand{\vw}{\bvec{w}}
\newcommand{\vz}{\bvec{z}}
\newcommand{\dif}{\mathsf{d}}
\newcommand{\hf}{\hat{f}}
\newcommand{\hS}{\widehat{S}}
\newcommand{\tS}{\widetilde{S}}
\newcommand{\tf}{\tilde{f}}
\newcommand{\fC}{\mathfrak{C}}
\newcommand{\homega}{\widehat{\omega}}
\newcommand{\wcomega}{\mathring{\omega}}
\newcommand{\vzero}{\bvec{0}}
\newcommand{\integers}{\mathbb{Z}}
\newcommand{\naturals}{\mathbb{N}}
\newcommand{\ip}[3][{}]{\ensuremath{\left \langle #2, #3 \right \rangle_{#1}}}
\newcommand\iid{\stackrel{iid}{\sim}}

@@

Each $\mathcal{P}_m$ has a group structure under the digit wise addition. Analogously, we can also define the dual nets as $\mathcal{P}_m^\perp=\{\vk\in\mathbb{N}_0^d:\ip{\vx}{\vk}=0,\, \vx\in\mathcal{P}_m\}$,
\[
\mathcal{P}_0^\perp=\left\{\mathbb{N}_0^d\right\}\supset\dots\supset\mathcal{P}_\infty=\{\bvec{0}\}.
\]

@@

In \cite{HicJim} we proposed an algorithm based on digital nets that estimates hight dimensional integrals whose error lies within a user-input error tolerance. This algorithm finds the number of data points automatically. We will refer to it as $\widehat{I}(f;\varepsilon)$, where $f$ is the function to integrate and $\varepsilon$ the user-input error tolerance.

@@

@@

The aim of our algorithm is to estimate the normalized Sobol' indices, $\underline{S}_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$. In both cases, regular and normalized indices can be approximated by estimating integrals,
\begin{align}\label{indices_integ_1}
\underline{S}_u & = \frac{\int_{[0,1)^{2d-1}} f(\vx)f(\vx_{u}:{\vx'}_{-u})d\vx d{\vx'} - \mu^2 }{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1-(I_3)^2}{I_2-(I_3)^2}, \\
\label{indices_integ_2}
\overline{S}_u & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1}{I_2-(I_3)^2}.
\end{align}
However, to guarantee the error in our $\underline{S}_u$ and $\overline{S}_u$ approximations we need to proceed with an estimator different than the usual. Given equations \eqref{indices_integ_1} and \eqref{indices_integ_2}, one may write $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$. According to section \ref{sec_reliable_error}, integrals can be estimated such that $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI}):=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$. Thus, the following estimator
\begin{align*}
\widehat{S}_u & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),0\right) \right) \\
\varepsilon_{S_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),0\right) \right)
\end{align*}
ensures that the true value $S_u\in [\widehat{S}_u - \varepsilon_{S_u}, \widehat{S}_u + \varepsilon_{S_u}]$.

>>>>

\newcommand{\fudge}{\fC}
\newcommand{\dtf}{\textit{\doubletilde{f}}}
\newcommand{\cube}{[0,1)^d}
%\renewcommand{\bbK}{\natzero^d}
\newcommand{\rf}{\mathring{f}}
\newcommand{\rnu}{\mathring{\nu}}
\newcommand{\natm}{\naturals_{0,m}}
\newcommand{\wcS}{\widecheck{S}}
\newcommand{\tol}{\text{tol}}
\newcommand{\e}{\text{e}}
\newcommand{\bvec}[1]{\boldsymbol{#1}}
\newcommand{\vx}{\bvec{x}}
\newcommand{\vt}{\bvec{t}}
\newcommand{\vI}{\bvec{I}}
\newcommand{\vk}{\bvec{k}}
\newcommand{\vw}{\bvec{w}}
\newcommand{\vz}{\bvec{z}}
\newcommand{\dif}{\mathsf{d}}
\newcommand{\hf}{\hat{f}}
\newcommand{\hS}{\widehat{S}}
\newcommand{\tS}{\widetilde{S}}
\newcommand{\tf}{\tilde{f}}
\newcommand{\fC}{\mathfrak{C}}
\newcommand{\homega}{\widehat{\omega}}
\newcommand{\wcomega}{\mathring{\omega}}
\newcommand{\vzero}{\bvec{0}}
\newcommand{\integers}{\mathbb{Z}}
\newcommand{\naturals}{\mathbb{N}}
\newcommand{\ip}[3][{}]{\ensuremath{\left \langle #2, #3 \right \rangle_{#1}}}
\newcommand\iid{\stackrel{iid}{\sim}}

@@

Each $\mathcal{P}_m$ has a group structure under the digit-wise addition:
\[
\vx\oplus\vt = \left(\sum_{\ell=1}^{\infty} [(x_{j\ell} + t_{j\ell}) \bmod b] b^{-\ell} \pmod{1} \right)_{j=1}^d.
\]
where $x_{j\ell}$ and $t_{j\ell}$ are the binary decompositions of $x_j$ and $t_j$.

 Analogously, we can also define the dual nets as $\mathcal{P}_m^\perp=\{\vk\in\mathbb{N}_0^d:\ip{\vx}{\vk}=0,\, \vx\in\mathcal{P}_m\}$,
\[
\mathcal{P}_0^\perp=\left\{\mathbb{N}_0^d\right\}\supset\dots\supset\mathcal{P}_\infty=\{\bvec{0}\}.
\]

@@

In \cite{HicJim} we proposed an ordering of the wavenumbers $\vk\in\naturals_0^d$ that led to the data-based upper bound below,

@@

 algorithm based on digital nets that estimates hight dimensional integrals whose error lies within a user-input error tolerance. This algorithm finds the number of data points automatically. We will refer to it as $\widehat{I}(f;\varepsilon)$, where $f$ is the function to integrate and $\varepsilon$ the user-input error tolerance.

@@

The aim of our algorithm is to estimate the normalized Sobol' indices, $\underline{S}_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$. In both cases, regular and normalized indices can be approximated by estimating integrals,
\begin{align}\label{indices_integ_1}
\underline{S}_u & = \frac{\int_{[0,1)^{2d-1}} \left(f(\vx)-
f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'} }{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1}{I_3-(I_4)^2}, \\
\label{indices_integ_2}
\overline{S}_u & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_2}{I_3-(I_4)^2}.
\end{align}
However, to guarantee the error in our $\underline{S}_u$ and $\overline{S}_u$ approximations we need to proceed with an estimator different than the usual. Given equations \eqref{indices_integ_1} and \eqref{indices_integ_2}, one may write $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$. According to section \ref{sec_reliable_error}, integrals can be estimated such that $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI}):=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$. Thus, the following estimator
\begin{align*}
\widehat{\underline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\right) \right) \\
\varepsilon_{\underline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\right) \right)
\end{align*}
\begin{align*}
\widehat{\overline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),0\right) \right) \\
\varepsilon_{\overline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),0\right) \right)
\end{align*}
ensures that the true value $S_u\in [\widehat{S}_u - \varepsilon_{S_u}, \widehat{S}_u + \varepsilon_{S_u}]$. Explain why max min 0, 1.............

\begin{figure}\centering
\includegraphics[width=1.\textwidth]{Images/scheme_S.eps}
%\caption*{Representation of estimators.}
\end{figure}
